Pyg4ometry: a python library for the creation of Monte Carlo particle transport physical geometries

### 2019-08-16 public/paper/pyg4ometry.tex
Paper update

%% The lineno packages adds line numbers. Start line numbering with
%% \begin{linenumbers}, end it with \end{linenumbers}. Or switch it on
%% for the whole article with \linenumbers after \end{frontmatter}.
%% \usepackage{lineno}

@@

\subsection{Geant Detector Mark-up Language} 
To exchange geometry descriptions Geant Detector Mark-up Language (GDML) was developed. Geant4 and ROOT can read and write GDML format and it is commonly
used as an exchange format for Geant4 geometries. 
\begin{table}[hbt!]
\centering
\begin{tabular}{|l|l|l|} \hline
GDML tag 		&  Child tags				& pyg4ometry class 				\\ \hline
define 			& constant				& gdml.Constant				\\
				& variable					& gdml.Variable					\\
				& quantity					& gdml.Quantity				\\
				& expression 				& gdml.Expression				\\
				& position					& gdml.Position					\\
				& rotation					& gdml.Rotation				\\
				& scale					& gdml.Scale					\\
				& matrix					& gdml.Matrix					\\
materials 			& element					& geant4.Element				\\
				& isotope					& geant4.Isotope				\\
				& material					& geant4.Material				\\
solid  			& box					& geant4.solid.Box				\\
	  			& tube					&							\\
	  			& cutTube					&							\\
	  			& cone					&							\\
	  			& para					&							\\
	  			& trd						&							\\
	  			& trap					&							\\
	  			& sphere					&							\\
	  			& orb					&							\\
	  			& torus					&							\\
	  			& polycone				&							\\
	  			& genericPolycone			&							\\
	  			& polyhedra				&							\\
	  			& eltube					&							\\
	  			& ellipsoid					&							\\
	  			& elcone					&							\\
				& paraboloid				&							\\
				& hype					& 							\\
				& tet						& 							\\
				& xtru					& 							\\
				& twistedbox				& 							\\
				& twistedtrap				& 							\\
				& twistedtrd				& 							\\
				& twistedtube				& 							\\
				& arb8					& 							\\
				& tesselated				& 							\\
				& union					& 							\\
				& subtraction				& 							\\
				& intersection				& 							\\
				& multiUnion				& 							\\
				& scaledSolid				&							\\				
	  			& opticalsurface			&							\\
structure			& volume					& geant4.LogicalVolume			\\
				& physvol					& geant4.PhysicalVolume			\\ 
				& replicavol				& geant4.ReplicaVolume			\\ 
				& paravol					& geant4.ParameterisedVolume	\\ 
				& divisionvol				& geant4.DivisionVolume			\\
				& skinsurface				& geant4.SkinSurface			\\ 
				& bordersurface			& geant4.BorderSurface			\\ \hline

@@

For a logical volume with $n_{\rm daughters}$ physical volumes, assuming meshes for solids with average number of vertices $n$, clearly this algorithm has complexity $\sim \mathcal{O}(n^2 n_{\rm daughters})$. This might seem like a prohibitive computational cost, but worth it considering the potential waste if small overlaps are present in the final 
PT simulation. This algorithm clearly favours geometry descriptions which have a high degree of logical volume reuse. Due to the discrete nature of triangular meshes it is not possible to have perfect detection of overlaps, especially when curved surfaces are considered.

@@

@@

>>>>

%% The lineno packages adds line numbers. Start line numbering with

%% \begin{linenumbers}, end it with \end{linenumbers}. Or switch it on
%% for the whole article with \linenumbers after \end{frontmatter}.
%% \usepackage{lineno}

@@

\subsection{Geant Detector Mark-up Language} 
To exchange geometry descriptions Geant Detector Mark-up Language (GDML) was developed. Geant4 and ROOT can read and write GDML format and it is commonly
used as an exchange format for Geant4 geometries. 
\begin{table}[hbt!]
\centering
\begin{tabular}{|l|l|l|} \hline
GDML tag 		&  Child tags				& pyg4ometry class 				\\ \hline
define 			& constant				& gdml.Constant				\\
				& variable					& gdml.Variable					\\
				& quantity					& gdml.Quantity				\\
				& expression 				& gdml.Expression				\\
				& position					& gdml.Position					\\
				& rotation					& gdml.Rotation				\\
				& scale					& gdml.Scale					\\
				& matrix					& gdml.Matrix					\\
materials 			& element					& geant4.Element				\\
				& isotope					& geant4.Isotope				\\
				& material					& geant4.Material				\\
solid  			& box					& geant4.solid.Box				\\
	  			& tube					&							\\
	  			& cutTube					&							\\
	  			& cone					&							\\
	  			& para					&							\\
	  			& trd						&							\\
	  			& trap					&							\\
	  			& sphere					&							\\
	  			& orb					&							\\
	  			& torus					&							\\
	  			& polycone				&							\\
	  			& genericPolycone			&							\\
	  			& polyhedra				&							\\
	  			& eltube					&							\\
	  			& ellipsoid					&							\\
	  			& elcone					&							\\
				& paraboloid				&							\\
				& hype					& 							\\
				& tet						& 							\\
				& xtru					& 							\\
				& twistedbox				& 							\\
				& twistedtrap				& 							\\
				& twistedtrd				& 							\\
				& twistedtube				& 							\\
				& arb8					& 							\\
				& tesselated				& 							\\
				& union					& 							\\
				& subtraction				& 							\\
				& intersection				& 							\\
				& multiUnion				& 							\\
				& scaledSolid				&							\\				
	  			& opticalsurface			&							\\
structure			& volume					& geant4.LogicalVolume			\\
				& assembly				& geant4.AssemblyVolume 		\\
				& physvol					& geant4.PhysicalVolume			\\ 
				& replicavol				& geant4.ReplicaVolume			\\ 
				& paravol					& geant4.ParameterisedVolume	\\ 
				& divisionvol				& geant4.DivisionVolume			\\
				& skinsurface				& geant4.SkinSurface			\\ 
				& bordersurface			& geant4.BorderSurface			\\ \hline

@@

@@

For a logical volume with $n_{\rm daughters}$ physical volumes, assuming meshes for solids with average number of vertices $n$, clearly this algorithm has complexity $\sim \mathcal{O}(n^2 n_{\rm daughters})$. This might seem like a prohibitive computational cost, but worth it considering the potential waste if small overlaps are present in the final 
PT simulation. This algorithm clearly favours geometry descriptions which have a high degree of logical volume reuse. Due to the discrete nature of triangular meshes it is not possible to have perfect detection of overlaps, especially when curved surfaces are considered. 
 \begin{figure}[htbp]
\begin{center}
\includegraphics[width=8cm]{./diagrams/overlap.pdf}
\caption{Placement of physical volume inside a logical volume}
\label{fig:lvToPv}
\end{center}
\end{figure}

@@

\begin{table}[hbt!]
\centering
\begin{tabular}{|l|l|l|} \hline
Fluka body			& note			& pyg4ometry class 				\\ \hline
RPP (done)			&				&							\\
BOX					&				&							\\
SPH (done)			&				&							\\
RCC (done)			&				&							\\
REC (done)			&				&							\\
TRC (done)			&				&							\\
ELL 					&				&							\\
WED					&				&							\\
RAW					&				&							\\
ARB					&				&							\\
XYP (done)			&				&							\\
XZP (done)			&				&							\\
YZP (done)			&				&							\\
PLA (done)			&				&							\\
XCC (done)			&				&							\\
YCC (done)			&				&							\\
ZCC (done)			&				&							\\
XEC (done)			&				&							\\
YEC (done)			&				&							\\
ZEC (done)			&				&							\\
QUA (done)			&				&							\\ \hline
\end{tabular}
\caption{Fluka geometry directives pyg4ometry classes.}
\end{table}
